\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
changes on progress
updates on progress

\medskip
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is \red{XX} $\times$ \red{XX} unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also includes no-flux across upper and lower boundaries. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).

Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.

\medskip
Another numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994} (\red{ .... COMMENT THE RESULTS OBTAINED AND COMPARE IT WITH EVANS WORK ...})

@@

All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs. In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$. For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$. Fluids are assumed incompressible and gravity was neglected. The set-up for the numerical simulations are summarised in Table \ref{table:setup}.

>>>>

\medskip
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also includes no-flux across upper and lower boundaries. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).

\medskip
Figures~\ref{fem_cv_represent_a}(a) and (b) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. The idea was to to study the effects of heterogeneity of a quadrant model geometry using the current element type. This, in large scale, is a problem that can be found in petroleum production.

\medskip
Another numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.

\medskip
Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. The flow profile follows the same behaviour with the experimental work of \citet{evans_1994}. In both cases the flow will not follow the standar source-sink behaviour. The mobility ratio (or VR) is playing a crucial role for these flows but the cross-flow pattern always occurs. The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow. In the current case the map of permeabilities is the same but reversed sto the main cross-flow is heading downwards instead of upwards.

 (\red{ .... COMMENT THE RESULTS OBTAINED AND COMPARE IT WITH EVANS WORK ...})

@@
